On Secure Delegation of SampBQP with a Classical Client

### 2020-02-09 blind.tex
Add notes from Skype discussion

\begin{thm}
	$\PiSampB$ has the same completeness and soundness guarantees as $\PiSamp$ and is blind.
\end{thm}
\begin{prf}
	The proof is identical to that of \cref{thm:BlindBQP} up to relabeling.
	Note that we don't have negligible soundness errors here, since $\PiSamp$ doesn't either; the proof only shows that the compiliation preserves soundness.
\end{prf}

>>>>

\begin{thm}
	$\PiSampB$ has the same completeness and soundness guarantees as $\PiSamp$ and is blind.
\end{thm}
\begin{prf}
	The proof is identical to that of \cref{thm:BlindBQP} up to relabeling.
	\Ethan{too hand-wavy still, can still say ``identically simulates"}
	Note that we don't have negligible soundness errors here, since $\PiSamp$ doesn't either; the proof only shows that the compiliation preserves soundness.
	\Ethan{Soundness def. is different}
\end{prf}

### 2020-02-09 bqp.tex
Add notes from Skype discussion

\def\blind{\mathsf{blind}}
\nc{\Piblind}{\ensuremath{\Pi_\blind}}
\nc{\Vblind}{\ensuremath{V_\blind}}
\nc{\Pblind}{\ensuremath{P_\blind}}
\nc{\Pblindstar}{\ensuremath{P_\blind^*}}
\nc{\cVblind}[1]{\ensuremath{\cV_{\blind,#1}}}
\nc{\cPblind}[1]{\ensuremath{\cP_{\MF,#1}}}

@@

@@

In this subsection we present our constant-round blind delegation protocol for $\BQP$. That is, proving this theorem:
\begin{thm}
	\label{thm:QPIP0BQP}
	There exists a constant-round and blind $\QPIP_0$ protocol for $\BQP$ with negligible completeness and soundness.
\end{thm}
We'll spend this section construct said protocol piece by piece, starting with the following $\QPIP_1$ protocol for $\BQP$.
We'll later construct a protocol for $\SampBQP$ following the same flow of logic, albeit requiring more careful analysis.

We start with a high-level description of the $\QPIP_1$ scheme $\PiMF$ from \cite{FOCS:Mahadev18a}, which is in turn taken from \cite{mf16}.

This is a one-message $\QPIP_1$ protocol with only $X$ and $Z$ measurement for deciding a $\BQP$ language $L$.
Roughly, on input $x\in\set{0,1}^n$, the prover sends a $m$-qubit certificate state $\rho$ to the verifier qubit-by-qubit.
The verifier samples a product measurement $\Lambda$ of $X$ and $Z$s according to a certain distribution, and applies it to $\rho$.
The verifier then, using the measurement results, decides whether to accept or reject.

\begin{protocol}{1-message $\QPIP_1$ protocol $\PiMF = (\PMF, \VMF)$ for $\BQP$ language $L$}
	\label{proto:BQP}
	Common input: $x\in\set{0,1}^n$. 
	\begin{enumerate}
		\item The prover generates a certificate state $\rho\leftarrow\cPMF{1}(x)$  and sends $\rho$ to the verifier qubit-by-qubit.
		\item The verifier generates $\Lambda \leftarrow \cVMF{2}(x)$, where $\Lambda=\Lambda_1\otimes\ldots\otimes\Lambda_m$;
			each $\Lambda_i$ is a single-qubit $X$ or $Z$ measurement and $m=\poly(n)$ is the length of the prover's certificate state.
			It applies $\Lambda$ to $\rho$ qubit-by-qubit.
			Let $w \in \set{0,1}^m$ denote the measurement outcome.
			It verifies the measurement outcome and produces a decision $o\leftarrow\cVMF{3}(x, \Lambda, w)$ where $o\in\set{acc, rej}$ and $\cVMF{3}$ is a classical polynomial-time algorithm.
	\end{enumerate}
\end{protocol}

$\PiMF$ has negligible completeness and soundness.

We compile $\PiMF$ using Mahadev's $\QHE$ from \cite{mahadev_qfhe} to obtain a blind 1-message $\QPIP_1$ protocol $\Piblind$ for $\BQP$, again with only $X$ and $Z$ measurements.
The high level idea is to run $\PiMF$ under $\mathsf{QHE}$.
Namely, the verifier encrypts its original input $x$ and sends $y=\mathsf{QHE.Enc}(x)$ to the prover.
The prover then homomorphically evaluates $\cF$ on $y$ to produce $\sigma$ and sends it to the verifier.

Now the verifier needs to obtain the measurement outcome $w$ from the encrypted state $\sigma$ using qubit-by-qubit $X$ and $Z$ measurements.
This may not be possible in general, but we observe that $\mathsf{QHE}$ allows this. 
Its ciphertexts consists of a Pauli one-time-padded plaintext and classically encrypted Pauli keys.
Pauli one-time-pads commute with $X$ and $Z$ measurements, so the verifier can measure the one-time-padded state as usual, then correct the measurement results using the Pauli keys.
Now we state and prove this observation in more precise terms.

\Ethan{TODO PROOFREAD ME}
\begin{thm}
	\label{decodeMeasureOrder}
	Let $n\in\bbN$.
	Let $m\in\bbN$ be the length of the ciphertexts under $\mathsf{QHE}$ corresponding to plaintexts of length $n$.

@@

Now we state our results of compiling $\PiMF$ using $\mathsf{QHE}$:

@@

	Let $d=\poly(n)$ be the depth of the circuit corresponding to $\cPMF{1}$.
	\begin{enumerate}
		\item The verifier generates $(pk, sk, evk)\leftarrow\mathsf{QHE.Keygen}(1^n, 1^d)$, where $d$ is the depth of the circuit corresponding to $\cPMF{1}(x)$.
			It then generates and sends $ct_x\leftarrow\mathsf{QHE.Enc}_{pk}(x)$ to the prover.
			It also sends $evk$ to the prover.
		\item The prover homomorphically evaluates $\cPMF{1}$ on input $ct_x$, generating $\sigma\leftarrow\mathsf{QHE.Eval}_{evk}(\cPMF{1}, ct_x)$.
			It sends $\sigma$ to the verifier qubit-by-qubit.
		\item The verifier generates $\Lambda\leftarrow\cVMF{2}(x)$,
			$\Lambda'\leftarrow\cM_\QHE$,
			$ct_w\leftarrow\Lambda'(\sigma)$,
			$w\leftarrow\widehat{\mathsf{QHE.Dec}_{sk}}(ct_w)$,
			and $o\leftarrow\cVMF{3}(x, \Lambda, w)$.
			It outputs $o$.
	\end{enumerate}
\end{protocol}

@@

	Suppose for the sake of contradiction that there exists some cheating prover $\Pblindstar$ with some noticeable acceptance probability $\varepsilon$.

	Then we can construct a prover $\PMFstar$ violating the soundness guarantees of $\PiMF$ by simulating $(\Vblind(x), \Pblindstar)$ as below:

	We define $\PMFstar$ to first generate
	$(pk, sk, evk)\leftarrow\mathsf{QHE.Keygen}(1^n, 1^d)$
	and
	$y\leftarrow\mathsf{QHE.Enc}_{pk}(x)$
	It then sends $y$ and $evk$ to $\Pblindstar$ and gets $\sigma$ back.
	Finally, it decrypts
	$\rho\leftarrow\mathsf{QHE.Dec}_{sk}(\sigma)$
	and sends it to $\VMF$ qubit-by-qubit.

	We now prove that $\PMFstar$ in fact violates the soundness of $\PiMF$.
	Let $\cP_\blind^*$ denote the action $\Pblindstar$ takes to produce $\sigma$ from $ct_x$.
	Consider the experiment corresponding to $\Piblind$:
	$$(pk, sk, evk)\leftarrow\QGen(1^n, 1^d)$$
	$$ct_x\leftarrow\QEnc_{pk}(x)$$
	$$\sigma\leftarrow\cP_\blind^*(ct_x, evk)$$
	$$\Lambda\leftarrow\cVMF{2}(x)$$
	$$\Lambda'\leftarrow\cM_\QHE(\Lambda)$$
	$$ct_w\leftarrow\Lambda'(\sigma)$$
	$$w\leftarrow\widehat{\QDec_{sk}}(ct_w)$$
	$$o\leftarrow\cVMF(x, \Lambda, w)$$

@@

	By inspection, the only difference between the experiments is how $w$ is obtained from $\sigma$.
	By \cref{decodeMeasureOrder}, the two ways are equivalent.
\end{prf}

>>>>

\def\blind{\mathsf{blind}}
\nc{\Piblind}{\ensuremath{\Pi_\blind}}
\nc{\Vblind}{\ensuremath{V_\blind}}
\nc{\Pblind}{\ensuremath{P_\blind}}
\nc{\Pblindstar}{\ensuremath{P_\blind^*}}
\nc{\cVblind}[1]{\ensuremath{\cV_{\blind,#1}}}
\nc{\cPblind}[1]{\ensuremath{\cP_{\blind,#1}}}

@@

\Ethan{Use only pk, sk and combine evk into pk}

@@

In this subsection we present our constant-round blind delegation protocol for $\BQP$. That is, proving this theorem:
\begin{thm}
	\label{thm:QPIP0BQP}
	There exists a constant-round and blind $\QPIP_0$ protocol for $\BQP$ with negligible completeness and soundness.
\end{thm}
We'll spend this section construct said protocol piece by piece, starting with the following $\QPIP_1$ protocol for $\BQP$.
\Ethan{Write outline here; highlight key ideas/steps}
We'll later construct a protocol for $\SampBQP$ following the same flow of logic, albeit requiring more careful analysis.
We start with a high-level description of the $\QPIP_1$ scheme $\PiMF$ from \cite{FOCS:Mahadev18a}, which is in turn taken from \cite{mf16}.

This is a one-message $\QPIP_1$ protocol $\PiMF$ with only $X$ and $Z$ measurement for deciding a $\BQP$ language $L$.
Roughly, on input $x\in\set{0,1}^n$, the prover sends a $m$-qubit certificate state $\rho$ to the verifier qubit-by-qubit.
The verifier samples a product measurement \Ethan{for consistency, ``measurement basis choice"} $\Lambda$ of $X$ and $Z$s according to a certain distribution, and applies it to $\rho$.
The verifier then, using the measurement results, decides whether to accept or reject.

\begin{protocol}{1-message $\QPIP_1$ protocol $\PiMF = (\PMF, \VMF)$ for $\BQP$ language $L$}
	\label{proto:BQP}
	Common input: $x\in\set{0,1}^n$. 
	\begin{enumerate}
		\item The prover generates a certificate state $\rho\leftarrow\cPMF{1}(x)$ and sends $\rho$ to the verifier qubit-by-qubit. \Ethan{Say it's $m$ qubits}
		\item The verifier generates $\Lambda \leftarrow \cVMF{2}(x)$, where $\Lambda=\Lambda_1\otimes\ldots\otimes\Lambda_m$;
			each $\Lambda_i$ is a single-qubit $X$ or $Z$ measurement.
			It applies $\Lambda$ to $\rho$ qubit-by-qubit.
			Let $w \in \set{0,1}^m$ denote the measurement outcome.
			It verifies the measurement outcome and produces a decision $o\leftarrow\cVMF{3}(x, \Lambda, w)$ where $o\in\set{acc, rej}$ and $\cVMF{3}$ is a classical polynomial-time algorithm.
	\end{enumerate}
\end{protocol}
\begin{thm}
    \Ethan{Add reference}
    $\PiMF$ has negligible completeness and soundness.
\end{thm}

We compile $\PiMF$ using Mahadev's $\QHE$ from \cite{mahadev_qfhe} to obtain a blind 1-message $\QPIP_1$ protocol $\Piblind$ for $\BQP$, again with only $X$ and $Z$ measurements.
The high level idea is to run $\PiMF$ under $\mathsf{QHE}$.
Namely, the verifier encrypts its original input $x$ and sends $y=\mathsf{QHE.Enc}(x)$ to the prover.
The prover then homomorphically evaluates $\cPMF{3}$ on $ct_x$ to produce $\sigma$ and sends it to the verifier.

Now the verifier needs to obtain the measurement outcome $w$ from the encrypted state $\sigma$ using qubit-by-qubit $X$ and $Z$ measurements.
This may not be possible in general, but we observe that Mahadev's $\mathsf{QHE}$ allows this. 
Its ciphertexts consists of a Pauli one-time-padded plaintext and classically encrypted Pauli keys.
Pauli one-time-pads commute with $X$ and $Z$ measurements, so the verifier can measure the one-time-padded state as usual, then correct the measurement results using the Pauli keys.
Now we state and prove this observation in more precise terms.

\Ethan{TODO PROOFREAD ME}
\begin{thm}
	\label{decodeMeasureOrder}
	Let $n\in\bbN$.
	Let $m\in\bbN$ be the length of the ciphertexts under $\mathsf{QHE}$ corresponding to plaintexts of length $n$. \Ethan{$m$ isn't well-defined this way; missing security param. and depth param.}

	\Ethan{Keygen here}

@@

Now we state our results of compiling $\PiMF$ using $\mathsf{QHE}$:
\Ethan{We state our construction of blind QPIP 1 for BQP by compiling...}

@@

	\begin{enumerate}
		\item The verifier generates $(pk, sk, evk)\leftarrow\mathsf{QHE.Keygen}(1^n, 1^d)$, where $d$ is the depth of the circuit corresponding to $\cPMF{1}(x)$.
			It then generates and sends $ct_x\leftarrow\mathsf{QHE.Enc}_{pk}(x)$ to the prover.
			It also sends $evk$ to the prover.
		\item The prover homomorphically evaluates $\cPMF{1}$ on input $ct_x$, generating $\sigma\leftarrow\cPblind{1}(evk, ct_x)=\mathsf{QHE.Eval}_{evk}(\cPMF{1}, ct_x)$.
			It sends $\sigma$ to the verifier qubit-by-qubit.
		\item The verifier generates $\Lambda\leftarrow\cVMF{2}(x)$,
			$\Lambda'\leftarrow\cM_\QHE(\Lambda)$,
			$ct_w\leftarrow\Lambda'(\sigma)$,
			$w\leftarrow\widehat{\mathsf{QHE.Dec}_{sk}}(ct_w)$,
			and $o\leftarrow\cVMF{3}(x, \Lambda, w)$.
			It outputs $o$.
	\end{enumerate}
\end{protocol}

@@

	Suppose for the sake of contradiction \Ethan{First specify this is for soundness proof} that there exists some cheating prover $\Pblindstar$ with some noticeable acceptance probability $\varepsilon$.
	Then we can construct a prover $\PMFstar$ violating the soundness guarantees of $\PiMF$ by simulating $(\Vblind(x), \Pblindstar)$ as below:

	We define $\PMFstar$ to first generate
	$(pk, sk, evk)\leftarrow\mathsf{QHE.Keygen}(1^n, 1^d)$
	and
	$y\leftarrow\mathsf{QHE.Enc}_{pk}(x)$
	It then sends $ct_x$ and $evk$ to $\Pblindstar$ \Ethan{Just run it, don't send it} and gets $\sigma$ back.
	Finally, it decrypts
	$\rho\leftarrow\mathsf{QHE.Dec}_{sk}(\sigma)$
	and sends it to $\VMF$ qubit-by-qubit.

	We now prove that $\PMFstar$ in fact violates the soundness of $\PiMF$.
	Let $\cP_\blind^*$ denote the action $\Pblindstar$ takes to produce $\sigma$ from $ct_x$.
	Consider the experiment corresponding to $(\Vblind, \Pblindstar)$:
	$$(pk, sk, evk)\leftarrow\QGen(1^n, 1^d)$$
	$$ct_x\leftarrow\QEnc_{pk}(x)$$
	$$\sigma\leftarrow\cP_\blind^*(ct_x, evk)$$
	$$\Lambda\leftarrow\cVMF{2}(x)$$
	$$\Lambda'\leftarrow\cM_\QHE(\Lambda)$$
	$$ct_w\leftarrow\Lambda'(\sigma)$$
	$$w\leftarrow\widehat{\QDec_{sk}}(ct_w)$$
	$$o\leftarrow\cVMF(x, \Lambda, w)$$

@@

    \Ethan{See google docs; remove the displayed math above and say in words}
	By inspection, the only difference between the experiments is how $w$ is obtained from $\sigma$.
	By \cref{decodeMeasureOrder}, the two ways are equivalent.
	\Ethan{Here finish the proof by contradiction. Something about epsilon.}
\end{prf}
